\documentclass[10pt]{article}
    \usepackage[margin = .5in]{geometry}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage{enumitem}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{2pt}
\begin{center}
	{\Huge \scshape {Jordan Wang}}\\
	jwang203@stevens.edu $\cdot$ Fort Lee, NJ $\cdot$ (973) 652-5128 $\cdot$ linkedin.com/in/jordan-wang-689146192/ $\cdot$ github.com/iFallenDawn \\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Stevens Institute of Technology}\hfill Hoboken, NJ\\
Bachelor of Science in Computer Science \textit{GPA: 3.919} \hfill August 2019 - Expected May 2023\\
\vspace{2mm}

%==== Skills ====%
\header{Skills}
	Java, Python, \LaTeX, Adobe Photoshop, Adobe Premiere                    \\
\vspace{2mm}

%==== Coursework ====%
\header{Coursework}
{\textbf{Relevant Courses}} {\sl August 2019 - May 2020} \hfill 
\\
Intro to Programming, Intro to Web Programming and Web Dev, Discrete Structures, Data Structures, Linear Algebra, Probability and Statistics\\
\vspace*{2mm}

{\textbf{Fall 2020}} {\sl August 2020 - December 2020} \hfill 
\\
Automata and Computation, Computer Organization and Programming, Algorithms, Project Management, Intermediate Statistics\\
\vspace*{2mm}
\ 

%==== Projects ====%
\header{Projects}
{\textbf{Ultimate Tic Tac Toe (2019)}} \hfill 
\\
Using Java, developed a variation of the classic game of Tic Tac Toe. Featured working Artificial Intelligence, hints, move list and a graph of ratings based off how well the game thinks the player is doing.\\
\vspace*{2mm}
{\textbf{FBLA Jeopardy (2019)}} \hfill 
\\
Using Java, designed a Jeopardy inspired game made to test the knowledge of FBLA members. Featured sound, five random categories chosen from a preset list of ten categories, and a team versus team experience.\\
\vspace*{2mm}
\ 
%==== Activities ====%
\header{Work Experience}
\vspace{1mm}
\textbf{Division of Information Technology} \hfill Stevens Institute of Technology\\
\textit{Student User Support Specialist} \hfill February 2020 - March 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Provided walk-in customer support and assisted in troubleshooting for students and professors experiencing issues with technology.
\end{itemize}

%==== Activities ====%
\header{Activities}
\vspace{1mm}

\textbf{Filipino Association of Stevens Tech (FAST)} \hfill Stevens Institute of Technology\\
\textit{Alumni Chair} \hfill August 2019 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Volunteered and attended various events such as ESC Around the World and Filipino Intercollegiate Networking Dialogue Fall Dialogue representing FAST.
	\item Helped with Public Relations involving events such as Mr. Philippines through photography and video editing using Adobe Photoshop and Adobe Premiere.
	\item Position on executive board attained April 2020.
\end{itemize}

\textbf{Ethnic Student Council (ESC)} \hfill Stevens Institute of Technology\\
\textit{Historian} \hfill April 2020 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Responsible for taking photos at ESC hosted events, bringing together various registered student organizations.
\end{itemize}

\textbf{Ultimate Frisbee Club Team} \hfill Stevens Institute of Technology\\
\textit{Photographer} \hfill August 2019 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Photographed and managed photo albums on DuckLink, a Stevens Institute of Technology managed website centered around finding organizations, attending events, and tracking involvement on campus.
\end{itemize}

\textbf{Future Business Leaders of America} \hfill Wayne Hills High School\\
\textit{Member} \hfill September 2018 - June 2019\\
\vspace{-1mm}
\begin{itemize}  \itemsep 1pt
	\item Competed in Six Flags Business and Marketing Day 2019 Challenge, winning Honorable Mention for successfully designing a career advertisement using Adobe Photoshop.
	\item Competed in FBLA State Leadership Conference 2019 for Computer Game and Simulation Programming.
\end{itemize}

%==== Extracurriculars ====%
\header{Extracurriculars}
Chinese Student Association, Society of Asian Scientists and Engineers, Korean Student Association
\end{document}